Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-04-14 paper/abstraction/paper.tex
tinker acks
added copyright
edits
fix typo in abstract

%% publication rights
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}  % default
%\setcopyright{rightsretained}

@@

\textbf{Abstract---}
We develop \sysname, a system to synthesize provably-correct
BGP (border gateway protocol) configurations for large, evolving networks from high-level
specifications of topology, routing policy, and fault-tolerance.
requirements. \sysname is based on new abstractions for capturing
parameterized network topologies and their evolution, and algorithms
to analyze the impact of topology and routing policy on fault
tolerance. Our algorithms operate entirely on abstract topologies.  We
prove that the properties established by our analyses hold for every
concrete instantiation of the given abstract topology. \sysname
also guarantees that only incremental changes to existing device configurations
are required when the network evolves to add or remove devices and
links. Our experiments with real-world topologies and policies show
that our abstractions and algorithms are effective, and that, for large
networks, \sysname synthesizes configurations two orders of magnitude
faster than systems that operate on concrete topologies.

@@

%\printccsdesc

@@

\para{Acknowledgments}
We thank the many network engineers, especially George Chen and Lihua Yuan, who pointed out the importance of working with abstract topologies. 
We also thank the PLDI reviewers, and especially our shepherd Alexandra Silva for comments on the paper. This work is supported in part by the National Science Foundation award CNS-1161595 as well as Cisco award 677002.

>>>>

%% publication rights
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}  % default
%\setcopyright{rightsretained}

@@

\textbf{Abstract---}
We develop \sysname, a system to synthesize provably-correct
BGP (border gateway protocol) configurations for large, evolving networks from high-level
specifications of topology, routing policy, and fault-tolerance
requirements. \sysname is based on new abstractions for capturing
parameterized network topologies and their evolution, and algorithms
to analyze the impact of topology and routing policy on fault
tolerance. Our algorithms operate entirely on abstract topologies.  We
prove that the properties established by our analyses hold for every
concrete instantiation of the given abstract topology. \sysname
also guarantees that only incremental changes to existing device configurations
are required when the network evolves to add or remove devices and
links. Our experiments with real-world topologies and policies show
that our abstractions and algorithms are effective, and that, for large
networks, \sysname synthesizes configurations two orders of magnitude
faster than systems that operate on concrete topologies.

@@

@@

\para{Acknowledgments}
We thank the many network engineers, especially George Chen and Lihua Yuan, who pointed out the importance of working with abstract topologies. 
We also thank the PLDI reviewers, and especially our shepherd Alexandra Silva for comments on the paper. This work is supported in part by the National Science Foundation award CNS-1161595 and Cisco award 677002.
